---
title: "Lab05 - Transformations for ANOVA"
output: pdf_document
---

## Goals

The goal in this lab is to practice working with transformations for ANOVA.

## Loading packages

Here are some packages with functionality you may need for this lab.  Run this code chunk now.

```{r, message = FALSE, warning=FALSE}
library(readr)
library(ggplot2)
library(gridExtra)
library(mosaic)
library(dplyr)
library(gmodels)

options("pillar.sigfig" = 10) # print 10 significant digits in summarize output
```

A gas chromatograph is an instrument that measures the amounts of various compounds contained in a sample by separating the various constituents.  The total number of counts recorded by the chromatograph is proportional to the amount of the compound present.

A calibration experiment was performed to see how the recorded counts from the chromatograph related to the concentration of a compound in a mixture and the flow rate through the chromatograph.  In this lab we will just look at the relationship between the concentration (explanatory variable) and the counts (response variable).

```{r}
chromatography <- read_csv("http://www.evanlray.com/data/sdm3/Chapter_29/Ch29_Chromatography.csv")
names(chromatography) <- c("concentration", "flow_rate", "counts")

chromatography %>%
  count(concentration)
```

#### 1. Make an appropriate plot of the data: it might be nice to use a histogram or density plot, separately for each value of cylinders. Also calculate the standard deviation for each group. Would it be appropriate to use an ANOVA model for these data?

```{r}

```

#### 2. Find a transformation of the data so that the ANOVA model would be appropriate.

```{r}

```

#### 2. Conduct a test of the claim that the mean count is the same for all three concentration levels.

```{r}

```

#### 3. Report and interpret an estimate of the difference in the centers of the distributions of counts for the high concentration and the low concentration, as well as a 95% confidence interval for that difference.  You should be able to do this in a few different ways.

```{r}

```
